## Loading the package 'BBmisc'
if(suppressMessages(!require('BBmisc'))) install.packages('BBmisc')
suppressMessages(library('BBmisc'))
pkgs <- c('tufte', 'knitr', 'rmarkdown', 'lubridate', 'plyr', 'dplyr', 'magrittr', 'purrr', 'stringr', 'stringi', 'wordcloud', 'slam', 'tm', 'igraph', 'NLP', 'xtable', 'SnowballC', 'rpart', 'RWeka', 'RColorBrewer', 'rvest', 'parallel', 'doParallel', 'ggplot2', 'googleVis', 'htmltools', 'rCharts', 'janeaustenr', 'syuzhet', 'viridis')
suppressAll(lib(pkgs)) 
## load in case of BBmisc::lib() doesn't work
suppressAll(plyr::l_ply(pkgs, require, quietly = TRUE))
rm(pkgs)
```

```{r setting-adjustment, echo=FALSE}
## Load BBmisc package again since there has error during knit (while working fine if run chunk-by-chunk)
suppressMessages(library('BBmisc'))
## Creating a parallel computing Cluster and support functions.
## Preparing the parallel cluster using the cores
doParallel::registerDoParallel(cores = 16)
#'@ BiocParallel::register(MulticoreParam(workers=8))
## Preparing the parallel cluster using the cores
suppressAll(library('parallel'))
jobcluster <- makeCluster(detectCores())
invisible(clusterEvalQ(jobcluster, library('tm')))
invisible(clusterEvalQ(jobcluster, library('RWeka')))
options(mc.cores = 2)
## Set the googleVis options first to change the behaviour of plot.gvis, so that only the chart 
##  component of the HTML file is written into the output file.
##  
## Set option to below if you want to plot an independent webpage with graph 
#'@ op <- options(gvis.plot.tag=NULL)
op <- options(gvis.plot.tag='chart')
## knitr configuration
# invalidate cache when the tufte version changes
suppressAll(library('knitr'))
opts_chunk$set(tidy = TRUE, fig.path = 'figure/', comment = NA, message = FALSE, fig.keep = 'high', fig.width = 10, fig.height = 6, fig.align = 'center', cache.extra = packageVersion('tufte'), echo = TRUE, progress = TRUE)
## Setting for rCharts
## http://ramnathv.github.io/posts/rcharts-nvd3/
options(warn = -1, htmltools.dir.version = FALSE, 
        rcharts.mode = 'iframesrc', rcharts.cdn = TRUE, 
        RCHART_WIDTH = 600, RCHART_HEIGHT = 400, 
        RCHART_TEMPLATE = 'Rickshaw.html', RCHART_LIB = 'morris')
```

```{r collect-data, echo=FALSE}
if(!file.exists('data/')) dir.create('data/')
lnk <- 'https://d396qusza40orc.cloudfront.net/dsscapstone/dataset/Coursera-SwiftKey.zip'
destfile <- 'Coursera-SwiftKey.zip'
if(!file.exists(paste0('data/', destfile))) {
  download.file(lnk, destfile = paste0('data/', destfile))
}
if(!file.exists(paste0('data/final'))) {
  ## Unzip the dataset
  #'@ unzip(paste0('data/', destfile), exdir = 'data/final/de_DE', list = TRUE)
  # Error in unzip(paste0("data/", destfile), exdir = "data/final/de_DE",  : 
  #   'exdir' does not exist
  unzip(paste0('data/', destfile), exdir = 'data/')
}
```

```{r project-files, echo=FALSE}
## Load plyr and dplyr packages again since there has error during knit (while working fine if run chunk-by-chunk)
suppressAll(library('plyr'))
suppressAll(library('dplyr'))
## files for this mile-stone report
lsfiles <- list.files('data/final/de_DE')
## summary of files
datafiles <- paste0('data/final/de_DE/', lsfiles)
rm(lsfiles)
```

```{r read-files-efficiency1, echo=FALSE}
## Load plyr and stringr packages again since there has error during knit (while working fine if run chunk-by-chunk)
suppressAll(library('plyr'))
suppressAll(library('stringr'))
## Creating a parallel computing Cluster and support functions.
## Preparing the parallel cluster using the cores
doParallel::registerDoParallel(cores = 16)
## http://www.r-bloggers.com/faster-files-in-r/
## 
## Run without parallel computing
## 
## readLines in normal way
suppressAll(
  dat1 <- llply(datafiles, function(x){
    readLines(x, encoding = 'UTF-8')                                    
  }))                                
```

```{r matching-data, echo=FALSE}
names(dat1) <- c('blogs', 'news', 'twitter')
## Delete the data folders to save the capacity.
unlink('data/final', recursive = TRUE)
#'@ dats <- c(dat1, dat1p, dat2, dat2p, dat3, dat3p, dat3s)
dats <- list(dat1)
suppressAll(rm(dat1))
## randomly take one data as sample files for further analysis
smp <- sample(dats, size=1) %>% unlist(recursive=FALSE)
```

```{r rm-objs2, include=FALSE}
rm(datafiles, dats)
```

```{r data-summary1, echo=FALSE}
suppressAll(library('stringi'))
cWords <- llply(smp, stri_count_words)
```

```{r arrange-data1, echo=FALSE}
mxSub <- llply(cWords, function(x) max(l
th(x)))
mxAll <- mxSub %>% unlist %>% max
chSub <- llply(mxSub, function(x) mxAll - x)
cWords1 <- llply(seq(cWords), function(i) {
  c(cWords[[i]], rep(0, chSub[[i]]))
  }) %>% data.frame(Line=seq(mxAll), .) %>% tbl_df
names(cWords1) <- c('Line', names(cWords))
rm(mxSub, mxAll, chSub)
```

```{r setting, message=FALSE}
suppressAll(library('googleVis'))
op <- options(gvis.plot.tag='chart')
```

```{r plot-hist1, result='asis'}
# Number of bins chosen automatically, which is sometimes bad
gvis.options <- list(legend="{ position: 'top', maxLines: 2 }",
                colors="['#5C3292', '#1A8763', '#871B47']",
                hAxis="{title:'names(cWords1)'}", width=600, height=400)
hist.gvis <- gvisHistogram(data=cWords1[sample(nrow(cWords1), 10000), names(cWords)], option=gvis.options, chartid='Histogram')
plot(hist.gvis)
```

```{r, results='asis'}
## Show gvis options
sapply(c("gvis.print.tag", "gvis.plot.tag", "gvis.tags"), getOption)
M <- gvisMotionChart(Fruits, "Fruit", "Year")
str(M)
```

```{r, results='asis'}
## The output for a complete web page
M
```

```{r, results='asis'}
## Access only the plot,
M$html$chart
```

```{r, results='asis'}
## wrap it in cat and it becomes more readable,
cat(unlist(M$html$chart))
```

```{r, results='asis'}
## or use the print function.
print(M, tag="chart")
```

```{r, results='asis'}
## Extract the data as a JavaScript function.
print(M, tag="jsData")
```

```{r, results='asis'}
## Display the visualisation.
## A web browser with Internet connection and Flash is required.
plot(M)
```

```{r, results='asis'}
## Combine with another chart, e.g. table
tbl <- gvisTable(Fruits, options=list(height=220))
Mtbl <- gvisMerge(M, tbl)
plot(Mtbl)
```

This is a little Markdown example file.
Set the googleVis options first.
In this case change the behaviour of plot.gvis

The following plot statements will automatically return the HTML
required for the 'knitted' output.

## Combo chart

```{r ComboExample, results='asis', tidy=FALSE}
## Add the mean
CityPopularity$Mean=mean(CityPopularity$Popularity)
CC <- gvisComboChart(CityPopularity, xvar='City',
yvar=c('Mean', 'Popularity'), options=list(seriesType='bars', width=450, height=300, title='City Popularity', series='{0: {type:\"line\"}}'))
plot(CC)
```

Example of gvisComboChart with R code shown above.

## Place two charts next to each other

```{r gvisMergeExample, results='asis', echo=FALSE}
Geo <- gvisGeoChart(Exports, locationvar='Country', colorvar='Profit',
options=list(height=300, width=350))
Tbl <- gvisTable(Exports, options=list(height=300, width=200))
plot(gvisMerge(Geo, Tbl, horizontal=TRUE))
```

Example of a gvisGeoChart with gvisTable and R code hidden.

## Motion Chart

```{r MotionChartExample, results='asis', tidy=FALSE}
M <- gvisMotionChart(Fruits, 'Fruit', 'Year',
options=list(width=400, height=350))
plot(M)
```

Please note that the Motion Chart is only displayed when hosted on a
web server, or is placed in a directory which has been added to the
trusted sources in the [security settings of Macromedia]
(http://www.macromedia.com/support/documentation/en/flashplayer/help/settings_manager04.html).
See the googleVis package vignette for more details.

```{r resetOptions}
## Set options back to original options
options(op)
```

# rCharts


